---
title: "HW1 document"
output: github_document
name: Binyue Hu
UNI: bh2849
---

```{r setup}
library(tidyverse)
```

## Problem 1

Let's load the 'penguins' dataset 

```{r}
data("penguins", package = "palmerpenguins")
```

#### a Short Description of the 'Penguins' dataset

Below we describe the dataset including names / values of important variables, the size of the dataset, and the mean flipper length.

```{r}
# It includes names / values of important variables
summary(penguins)
```

#### the Size of the Dataset 

```{r}
#the number of rows in 'penguins'
nrow(penguins)
#the number of columns in 'penguins'
ncol(penguins)
```

#### the Mean Flipper Length
```{r}
mean(pull(penguins,flipper_length_mm),na.rm = TRUE)
```

Let's make a scatterplot

#### Make a Scatterplot
```{r}

penguins %>%
ggplot(aes(bill_length_mm, flipper_length_mm, color = species)) +
    geom_point()

ggsave("scatter_plot.pdf",height = 4, width = 6)

```

## Problem 2

#### Dataframe 
```{r}
problem2_df = 
  tibble(
    random_samp = rnorm(10),
    var_logical = random_samp > 0,
    var_char = c("A","B","C","D","E","F","G","H","I","J"),
    var_factor = factor(c("Red","Red","Blue", "Red","Blue","Red","Blue", "Black","Black","Black"))
  )

show(problem2_df)
```

#### Mean of Each Variable of Dateframe
```{r}
mean(pull(problem2_df, random_samp))
mean(pull(problem2_df, var_logical))
mean(pull(problem2_df, var_char))
mean(pull(problem2_df, var_factor))
```
#### Convert Variables to Numeric Factors 
Logical vector can be convert to numeric vector because it has two options and they are able to calculate the mean. 

Character vector is not able to be calculated for the mean or convert to numeric vector.

Factor vector can be assigned different numbers for the different levels, and it can be calculated for the mean.
```{r}
convert_logical = as.numeric(pull(problem2_df, var_logical))

convert_char = as.numeric(pull(problem2_df, var_logical))

convert_factor = as.numeric(pull(problem2_df, var_factor))

```

